Query Optimization for Dynamic Imputation

### 2017-06-30 paper/experiments.tex
paper: conform to camera ready style
some changes for camera-ready, see slack post

\begin{table*}
  \centering
  \begin{subtable}{0.3\textwidth}
    \centering
    \input{tables/cdc_demo}
    \caption{Demographics (\texttt{demo}). \demorows{} rows.}
  \end{subtable}\quad\begin{subtable}{0.3\textwidth}
    \centering
    \input{tables/cdc_labs}
    \caption{Laboratory Results (\texttt{labs}). \labexrows{} rows.}
  \end{subtable}\quad\begin{subtable}{0.3\textwidth}
    \centering
    \input{tables/cdc_exams}
    \caption{Physical Results (\texttt{exams}). \labexrows{} rows.}
  \end{subtable}
  \caption{Percentage of values missing in the CDC NHANES 2013--2014 data.}\label{table:nhanes-description} 
\end{table*}

@@

\begin{table}
  \centering
  \input{tables/fcc}
  \caption{Percentage of values missing in the freeCodeCamp Survey data (\texttt{fcc}).}\label{table:fcc-description} 
\end{table}

@@

The queries consist not only of projections and selections, but also
interesting joins and aggregates. Our aim was to craft meaningful queries that would
provide performance figures relevant to practitioners using similar datasets.
\review{
Our benchmark queries performed well for both cases of \texttt{AVG} and \texttt{COUNT} aggregates, 
so we expect \ProjectName{} to perform similarly for \texttt{SUM}, with 
errors proportional to the fraction of relevant tuples retrieved and the \texttt{AVG} value estimated.}

@@

\begin{table*}
  \centering
  \input{queries}
  \vspace{1ex}
  \caption{Queries used in our experiments.}\label{tbl:queries}
\end{table*}

@@

\begin{table}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$ parameterizations, as compared to the baseline.
Queries optimized
    for quality ($\alpha=0$) generally achieve lower error than queries optimized for
    efficiency ($\alpha=1$). With ($\alpha=0.5$), an intermediate plan may be chosen if
    available.
    The count fraction column shows the number of tuples used in calculating each aggregate
     as a fraction of the number of tuples used when running the same query after imputing on the base table.
    A lower count share reflects more potential for errors.}
\label{table:smape}
\end{table}

@@

\textbf{Approximate Pareto Sets}\quad
However, \ProjectName{}'s planning algorithm is still exponential in the number of joins in the plan, and the use of Pareto sets exacerbates this exponential growth.
We explored the limits of our planning algorithm by constructing a series of queries with increasing number of joins over the CDC tables.
Planning times for queries involving 1--5 joins---a practical value for  real world exploratory queries---are less than 1 second.
We extended \ProjectName{} to support an approximation of Pareto sets to improve planning times for queries with 6 or more joins. Approximate Pareto sets
displayed a reduction in planning time linear with respect to the reduction in size of the final frontier. For queries with 6--8 joins, approximate sets achieved a reduction
in planning time between 14\% and 23\%, on average. Users can increase the level of approximation to reduce planning times further.

>>>>

\begin{table*}
  \centering
  \captionsetup{labelfont=bf}
  \caption{Percentage of values missing in the CDC NHANES 2013--2014 data.}\label{table:nhanes-description}
  \captionsetup{labelfont=up}
  \begin{subtable}{0.3\textwidth}
    \centering
    \caption{Demographics (\texttt{demo}). \demorows{} rows.}
    \input{tables/cdc_demo}
  \end{subtable}\quad\begin{subtable}{0.3\textwidth}
    \centering
    \caption{Laboratory Results (\texttt{labs}). \labexrows{} rows.}
    \input{tables/cdc_labs}
  \end{subtable}\quad\begin{subtable}{0.3\textwidth}
    \centering
    \caption{Physical Results (\texttt{exams}). \labexrows{} rows.}
    \input{tables/cdc_exams}
  \end{subtable}
\end{table*}

@@

\begin{table}
  \centering
  \captionsetup{labelfont=bf}
  \caption{Percentage of values missing in the freeCodeCamp Survey data (\texttt{fcc}).}\label{table:fcc-description}
  \input{tables/fcc}
\end{table}

@@

The queries consist not only of projections and selections, but also
interesting joins and aggregates. Our aim was to craft meaningful queries that would
provide performance figures relevant to practitioners using similar datasets.
\review{
Our benchmark queries performed well for both cases of \texttt{AVG} and \texttt{COUNT} aggregates, 
so we expect \ProjectName{} to perform similarly for \texttt{SUM}, with 
errors proportional to the fraction of relevant tuples retrieved and the \texttt{AVG} value estimated.}
\cameraready{Aggregates such as \texttt{MAX} and \texttt{MIN} are unlikely to perform well with dynamic imputation,
a difficulty carried over from traditional imputation and compounded by the dynamic nature 
of our approach.}

@@

\begin{table*}
  \centering
  \captionsetup{labelfont=bf}
  \caption{Queries used in our experiments.}\label{tbl:queries}
  \input{queries}
\end{table*}

@@

\begin{table}
  \centering
  \captionsetup{labelfont=bf}
  \caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$ parameterizations, as compared to the baseline.
    Queries optimized
    for quality ($\alpha=0$) generally achieve lower error than queries optimized for
    efficiency ($\alpha=1$). With ($\alpha=0.5$), an intermediate plan may be chosen if
    available.
    The count fraction column shows the number of tuples used in calculating each aggregate
    as a fraction of the number of tuples used when running the same query after imputing on the base table.
    A lower count share reflects more potential for errors.}\label{table:smape}
  \input{tables/perf_summary.tex}
\end{table}

@@

\textbf{Approximate Pareto Sets}\quad
However, \ProjectName{}'s planning algorithm is still exponential in the number of joins in the plan, and the use of Pareto sets exacerbates this exponential growth.
We explored the limits of our planning algorithm by constructing a series of queries with increasing number of joins over the CDC tables.
Planning times for queries involving 1--5 joins---a practical value for  real world exploratory queries---are less than 1 second.
We extended \ProjectName{} to support an approximation of Pareto sets to improve planning times for queries with 6 or more joins. Approximate Pareto sets
displayed a reduction in planning time linear with respect to the reduction in size of the final frontier. For queries with 6--8 joins, approximate sets achieved a reduction
in planning time between 14\% and 23\%, on average. \cameraready{For 6 joins, this is
a decrease from a mean planning time of 3.3 seconds to 2.5 seconds. For 7 joins, the decrease was from 14.2 to 12.2 seconds, while for 8 joins, it was
from 60 to 49 seconds.} Users can increase the level of approximation to reduce planning times further.
